\chapter{Flows and Logs Analysis}
\section{Complete 5G Call Flows and Logs}
\label{sec:appendix-call-flows}

This section provides access to the 5G call-flow diagrams and raw logs generated
during the multi-UPF deployment tests. Each call-flow PDF corresponds to a specific
\texttt{IMSI} and includes detailed message exchanges (registration, PDU session 
establishment, release procedures, etc.). Additionally, an optional raw log file 
(\texttt{e2eCallflows.log}) contains a plain-text record of all signaling steps.

\begin{table}[H]
\centering
\caption{Call Flow Files with IMSI References}
\begin{tabular}{ll}
\toprule
\textbf{IMSI} & \textbf{Call Flow PDF Link} \\
\midrule
208930100007500 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007500.pdf}{\texttt{View PDF}} \\
208930100007560 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007560.pdf}{\texttt{View PDF}} \\
208930100007620 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007620.pdf}{\texttt{View PDF}} \\
208930100007680 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007680.pdf}{\texttt{View PDF}} \\
208930100007750 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007750.pdf}{\texttt{View PDF}} \\
208930100007880 & \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/call_flow-imsi-208930100007880.pdf}{\texttt{View PDF}} \\
\bottomrule
\end{tabular}
\end{table}

\noindent
\textbf{Raw Log File (Optional).}  
\label{logs:e2eCallflows}
The plain-text log file listed below contains complete end-to-end call flows including 
NAS messages, authentication steps, security mode commands, and success indicators 
for each procedure:

\begin{itemize}
  \item \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/e2eCallflows.log}{\texttt{e2eCallflows.log}}
\end{itemize}

\noindent
These files capture the step-by-step message exchanges observed in the multi-UPF 
deployment. For details on how these logs were parsed and analyzed programmatically,
see Section~\ref{sec:analysis-scripts}.

\section{Analysis Scripts and Code Repositories}
\label{sec:analysis-scripts}

This section provides links to the Python/Jupyter notebooks used for automated logs 
analysis and call-flow interpretation. The notebooks are publicly accessible on GitHub 
for transparency and reproducibility.

\subsection{Logs Analysis}
The first notebook parses and analyzes 5G logs from both the Quick Start and Full 
Aether deployments, extracting key metrics (e.g., procedure latencies, success/failure 
counts) to produce summary statistics:

\begin{itemize}
    \item \textbf{GitHub Link:}
    \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/LogsAnalysis.ipynb}{\texttt{LogsAnalysis.ipynb (GitHub)}}
\end{itemize}

\noindent
Readers may either view it directly on GitHub or clone the repository to open it locally 
in Jupyter or a compatible environment.

\subsection{Call Flow Analysis}
A second notebook specifically focuses on visualizing call-flow sequences, including 
registration, PDU session establishment, service requests, and deregistrations. It reads
the detailed logs to highlight message sequences and timings:

\begin{itemize}
    \item \textbf{GitHub Link:}
    \href{https://github.com/hxngillani/Thesis-2025/blob/d0960d3a9d816eca167b428b2a6cfdfa707a49eb/Logs%26CallFlows%20Analysis/CallFlowsAnalysis.ipynb}{\texttt{CallFlowsAnalysis.ipynb (GitHub)}} 
\end{itemize}

\noindent
This notebook also generates message-sequence charts to illustrate how different UEs 
progress through various 5G procedures.

\paragraph{How to Use the Notebooks}
\begin{enumerate}
    \item \textbf{Clone the Repository:}
    \texttt{git clone https://github.com/hxngillani/Thesis-2025.git}
    \item \textbf{Install Dependencies:}
    Ensure you have Python 3 and Jupyter installed. Then install any additional
    libraries (e.g., \texttt{pandas}, \texttt{numpy}, \texttt{matplotlib}) using:
\begin{verbatim}
pip install -r requirements.txt
\end{verbatim}

    \item \textbf{Run Jupyter:}
    In the project directory, run \texttt{jupyter notebook} (or \texttt{jupyter lab})
    and open either \texttt{LogsAnalysis.ipynb} or \texttt{CallFlowsAnalysis.ipynb}.
\end{enumerate}

\noindent
These notebooks provide a reproducible way to examine the data collected from the
Aether deployments, confirm key metrics, and visualize the message flows. This approach
supports transparent testing, validation, and potential extensions for future research.
